Contextual recruitment of selective attention can be updated via changes in task-relevance

### 2019-01-23 manuscript.tex
update

\shorttitle{Contextual recruitment of selective attention}
\affiliation{
\vspace{0.5cm}
\textsuperscript{1} The Graduate Center of the City University of New York\\\textsuperscript{2} Brooklyn College of the City University of New York}
\keywords{Attention, Memory, Cognitive Control, Conflict Adaptation, Context-specific, Task Relevance\newline\indent Word count: 4024 \vspace{2mm} \par \textit{Public Significance Statement:} Contextual cues have been shown to automatically trigger adjustments in selective attention independent of awareness and intention. Here, we find the task-relevance plays an important role in determining which context cues are used to direct attention. These findings contribute to a better understanding of how context-dependency might occur in more complex environments and more generally, how learning and memory processes enable flexible control over attention.}
\usepackage{csquotes}
\usepackage{upgreek}
\captionsetup{font=singlespacing,justification=justified}

@@

\makeatletter
\newcommand\LastLTentrywidth{1em}
\newlength\longtablewidth
\setlength{\longtablewidth}{1in}
\newcommand{\getlongtablewidth}{\begingroup \ifcsname LT@\roman{LT@tables}\endcsname \global\longtablewidth=0pt \renewcommand{\LT@entry}[2]{\global\advance\longtablewidth by ##2\relax\gdef\LastLTentrywidth{##2}}\@nameuse{LT@\roman{LT@tables}} \fi \endgroup}

\usepackage{setspace}\doublespacing
\newenvironment{zeroindent} {\par\setlength{\parindent}{0pt}} {\par}
\setlength{\parskip}{0pt}
\raggedbottom

@@

\abstract{
Evidence across a wide variety of attention paradigms shows that
environmental cues can trigger adjustments to ongoing priorities for
attending to relevant and irrelevant information. This context-specific
control over attention suggests that cognitive control can be both
automatic and flexible. For instance, in selective attention tasks,
congruency effects are larger for items that appear in a context
associated with infrequent conflict than in a context associated with
frequent conflict. Since the to-be-presented context cannot be predicted
or prepared for in advance, attention is assumed to be rapidly updated
on-the-fly, triggered by the currently presented context.
Context-specific control exemplifies how learning and memory processes
can influence attention to enable cognitive flexibility. However, what
determines the use of previously learned associations still remains
unclear. In the current study, we examined whether task-relevance would
influence the learning and use of context cues in a flanker task. Using
a secondary counting task, context dimensions associated with differing
levels of conflict were made task-relevant or -irrelevant across the
experiment. In short, we found that making new contextual information
task-relevant caused participants to ignore a previously learned
context-attention association and adopt a new context-specific control
strategy; all without changing the experimental stimuli. This result
suggests that task-relevance is a key determinant of context-specific
control. 
}

@@

Selective attention is commonly investigated using interference
paradigms such as the Stroop (1935) and flanker (B. A. Eriksen \&
Eriksen, 1974) tasks, where participants identify a target while
ignoring a response-congruent or -incongruent distractor. Performance is
typically better on congruent versus incongruent trials and the
difference---the congruency effect---taken as an index of attentional
priorities. Large congruency effects are thought to reflect ineffective
filtering of the distracting stimuli whereas small congruency effects
are thought to reflect effective filtering. By probing factors that
systematically alter congruency effects, we can then make inferences
about processes that control attentional filtering. For example,
manipulating the frequency of conflict via the proportion of congruent
versus incongruent trials has shown to influence the size of the
congruency effect. Typically, a high proportion congruent experiment
produces large congruency effects, whereas a low proportion congruent
experiment produces small congruency effects (Logan \& Zbrodoff, 1979;
Lowe \& Mitterer, 1982; West \& Baylis, 1998). This result is usually
explained as strategic control, where participants increase attentional
control under high-conflict demands and relax attentional control under
low-conflict demands (Logan, 1980; Logan \& Zbrodoff, 1979; Logan,
Zbrodoff, \& Williamson, 1984; Lowe \& Mitterer, 1982). Recent work
however, has demonstrated that attentional control is not only adjusted
by top-down regulation, but can also be triggered automatically by
environmental cues (Brosowsky \& Crump, 2018; Bugg \& Crump, 2012;
Egner, 2014; Fischer \& Dreisbach, 2015; King, Korb, \& Egner, 2012;
Mayr \& Bryck, 2007).

For example, Crump, Gong, and Milliken (see also, Corballis \& Gratton,
2003; Crump, Gong, \& Milliken, 2006) presented Stroop stimuli in one of
two randomly chosen locations and manipulated the frequency of conflict
associated with each location. One location was associated with a high
frequency of conflict (25\% congruent trials) and the other with a low
frequency of conflict (75\% congruent trials). Overall, the proportion
of congruent trials was 50\% and randomized such that the upcoming
location could not be predicted. Even so, congruency effects were shown
to be smaller for trials where the stimulus appeared in the high
conflict location as compared to the low conflict location. This effect,
known now as the context-specific proportion congruent effect (CSPC),
has now been replicated in a number of different selective attention
paradigms (e.g., Alards-Tomalin, Brosowsky, \& Mondor, 2017; Blais,
Harris, Sinanian, \& Bunge, 2015; Bugg, 2014; Crump, 2016; Crump,
Milliken, Leboe-McGowan, Leboe-McGowan, \& Gao, 2018; Fischer,
Gottschalk, \& Dreisbach, 2014; Hübner \& Mishra, 2016).

Critical evidence however, that CSPC effects reflect context-specific
control rather than other non-control learning processes (e.g., Schmidt
\& Besner, 2008), comes from work showing that CSPC effects can transfer
to frequency unbiased items (Brosowsky \& Crump, 2016; Crump \&
Milliken, 2009; though, see Hutcheon \& Spieler, 2017; Weidler \& Bugg,
2016; Weidler, Dey, \& Bugg, 2018). Crump and Milliken (2009), for
example, divided Stroop items into two mutually exclusive sets (e.g.,
RED/GREEN and BLUE/YELLOW). One set was defined as the frequency biased
set, and presented with 75\% congruency in one location, and 25\%
congruency in the other. The second set however, was presented with 50\%
congruency in both locations. Nevertheless, they found smaller
congruency effects for unbiased items presented in the high conflict
location as compared to the low conflict location.

@@

\section{The Current Study}\label{the-current-study}

@@

A flanker task was used to measure attentional control in an adapted
CSPC design (Crump \& Milliken, 2009; Crump, Brosowsky, \& Milliken,
2017). Similar to previous studies, flanker stimuli were presented in
contexts associated with differing levels of conflict (0\%, 50\%, or
100\% congruent). However, unlike previous CSPC designs where contexts
were defined by a single discriminating feature (e.g., upper vs.~lower
screen locations), contexts were defined by two feature dimensions (see
Figure 1A). In one condition, for example, contexts were defined by
object identity (hat or chair) and color (blue or green). Only three out
of the four possible feature combinations were presented, each
associated with a different proportion of congruent trials (0\%, 50\%,
or 100\% congruent). Critically, the frequency unbiased context (50\%
congruent) always shared a feature with each of the frequency-biased
contexts (0\% and 100\% congruent). The frequency biased contexts (0\%
and 100\% congruent) however, did not share any features (see Figure 1C
for an example).

@@

\section{Methods}\label{methods}

@@

\subsection{Participants}\label{participants}

@@

\subsection{Apparatus \& Stimuli}\label{apparatus-stimuli}

@@

\subsection{Design}\label{design}

@@

\section{Results}\label{results}

@@

\section{General Discussion}\label{general-discussion}

@@

In light of prior work, we take this as evidence that the contextual
recruitment of selective attention, although likely implicit, is not
obligatory (e.g., Brosowsky \& Crump, 2016), requiring that
environmental information be incorporated into the task representation.
Similarly, there appears to be flexibility in which environmental
features are selected and used to guide attention, which can be rapidly
updated depending on the task-relevance of those features. Such a result
lends some insight into how context-specific control might operate in
more complex, real-world environments, where there is an over-abundance
of environmental features that afford many different learned
associations. From a theoretical perspective, this result is consistent
memory-based accounts of CSPC phenomena (Brosowsky \& Crump, 2018; Bugg
\& Hutchison, 2013; Crump \& Milliken, 2009; Crump et al., 2018, 2017).
Under this view, a memory process encodes attentional priorities in the
representation of individual experiences and, as a result, become
associated with the environment where they were used. The subsequent
reoccurrence of a prior context triggers the retrieval and reinstatement
of those attentional priorities. Our results show however, that all the
features of the environment may not be treated equally and that only
task-relevant features are used to probe memory and guide attention.

@@

\hypertarget{refs}{}
\hypertarget{ref-abrahamse_grounding_2016}{}
Abrahamse, E., Braem, S., Notebaert, W., \& Verguts, T. (2016).
Grounding cognitive control in associative learning. \emph{Psychological
Bulletin}, \emph{142}, 693--728.
doi:\href{https://doi.org/10.1037/bul0000047}{10.1037/bul0000047}

\hypertarget{ref-alards-tomalin_auditory_2017}{}
Alards-Tomalin, D., Brosowsky, N. P., \& Mondor, T. A. (2017). Auditory
statistical learning: Predictive frequency information affects the
deployment of contextually mediated attentional resources on perceptual
tasks. \emph{Journal of Cognitive Psychology}, \emph{29}, 977--987.
doi:\href{https://doi.org/10.1080/20445911.2017.1353518}{10.1080/20445911.2017.1353518}

\hypertarget{ref-blais_trial-by-trial_2015}{}
Blais, C., Harris, M. B., Sinanian, M. H., \& Bunge, S. A. (2015).
Trial-by-trial adjustments in control triggered by incidentally encoded
semantic cues. \emph{The Quarterly Journal of Experimental Psychology},
\emph{68}, 1920--1930.
doi:\href{https://doi.org/10.1080/17470218.2014.1000346}{10.1080/17470218.2014.1000346}

\hypertarget{ref-brady_visual_2013}{}
Brady, T. F., Konkle, T., Gill, J., Oliva, A., \& Alvarez, G. A. (2013).
Visual long-term memory has the same limit on fidelity as visual working
memory. \emph{Psychological Science}, \emph{24}, 981--990.
doi:\href{https://doi.org/10.1177/0956797612465439}{10.1177/0956797612465439}

\hypertarget{ref-brewer_dual_1988}{}
Brewer, M. B. (1988). A dual process model of impression formation. In
R. S. Wyer Jr \& T. K. Srull (Eds.), \emph{A dual-process model of
impression formation: Advances in social cognition} (Vol. 1, pp. 1--36).
Hillsdale, NJ: Erlbaum.

\hypertarget{ref-brosowsky_context-specific_2016}{}
Brosowsky, N. P., \& Crump, M. J. (2016). Context-specific attentional
sampling: Intentional control as a pre-requisite for contextual control.
\emph{Consciousness and Cognition}, \emph{44}, 146--160.
doi:\href{https://doi.org/10.1016/j.concog.2016.07.001}{10.1016/j.concog.2016.07.001}

\hypertarget{ref-brosowsky_memory-guided_2018}{}
Brosowsky, N. P., \& Crump, M. J. C. (2018). Memory-guided selective
attention: Single experiences with conflict have long-lasting effects on
cognitive control. \emph{Journal of Experimental Psychology: General},
\emph{147}, 1134--1153.
doi:\href{https://doi.org/10.1037/xge0000431}{10.1037/xge0000431}

\hypertarget{ref-bugg_conflict-triggered_2014}{}
Bugg, J. (2014). Conflict-triggered top-down control: Default mode, last
resort, or no such thing? \emph{Journal of Experimental Psychology:
Learning, Memory, and Cognition}, \emph{40}(2), 567.

\hypertarget{ref-bugg_support_2012}{}
Bugg, J., \& Crump, M. J. (2012). In support of a distinction between
voluntary and stimulus-driven control: A review of the literature on
proportion congruent effects. \emph{Frontiers in Psychology}, \emph{3},
367.
doi:\href{https://doi.org/10.3389/fpsyg.2012.00367}{10.3389/fpsyg.2012.00367}

\hypertarget{ref-bugg_converging_2013}{}
Bugg, J., \& Hutchison, K. A. (2013). Converging evidence for control of
color--word Stroop interference at the item level. \emph{Journal of
Experimental Psychology: Human Perception and Performance},
\emph{39}(2), 433.

\hypertarget{ref-bugg_multiple_2008}{}
Bugg, J., Jacoby, L. L., \& Toth, J. P. (2008). Multiple levels of
control in the Stroop task. \emph{Memory \& Cognition}, \emph{36},
1484--1494.
doi:\href{https://doi.org/10.3758/MC.36.8.1484}{10.3758/MC.36.8.1484}

\hypertarget{ref-canadas_social_2013}{}
Cañadas, E., Rodríguez-Bailón, R., Milliken, B., \& Lupiáñez, J. (2013).
Social categories as a context for the allocation of attentional
control. \emph{Journal of Experimental Psychology: General}, \emph{142},
934--943. doi:\href{https://doi.org/10.1037/a0029794}{10.1037/a0029794}

\hypertarget{ref-corballis_independent_2003}{}
Corballis, P. M., \& Gratton, G. (2003). Independent control of
processing strategies for different locations in the visual field.
\emph{Biological Psychology}, \emph{64}, 191--209.
doi:\href{https://doi.org/10.1016/S0301-0511(03)00109-1}{10.1016/S0301-0511(03)00109-1}

\hypertarget{ref-crisp_multiple_2007}{}
Crisp, R. J., \& Hewstone, M. (2007). Multiple social categorization.
\emph{Advances in Experimental Social Psychology}, \emph{39}, 163--254.

\hypertarget{ref-crump_learning_2016}{}
Crump, M. J. (2016). Learning to selectively attend from
context-specific attentional histories: A demonstration and some
constraints. \emph{Canadian Journal of Experimental Psychology/Revue
Canadienne de Psychologie Expérimentale}, \emph{70}, 59--77.
doi:\href{https://doi.org/10.1037/cep0000066}{10.1037/cep0000066}

\hypertarget{ref-crump_flexibility_2009}{}
Crump, M. J. C., \& Milliken, B. (2009). The flexibility of
context-specific control: Evidence for context-driven generalization of
item-specific control settings. \emph{The Quarterly Journal of
Experimental Psychology}, \emph{62}, 1523--1532.
doi:\href{https://doi.org/10.1080/17470210902752096}{10.1080/17470210902752096}

\hypertarget{ref-crump_context-dependent_2018}{}
Crump, M. J. C., Milliken, B., Leboe-McGowan, J., Leboe-McGowan, L., \&
Gao, X. (2018). Context-Dependent Control of Attention Capture: Evidence
From Proportion Congruent Effects. \emph{Canadian Journal of
Experimental Psychology= Revue Canadienne de Psychologie Experimentale},
\emph{74}, 91--104.

\hypertarget{ref-crump_reproducing_2017}{}
Crump, M. J., Brosowsky, N. P., \& Milliken, B. (2017). Reproducing the
location-based context-specific proportion congruent effect for
frequency unbiased items: A reply to Hutcheon and Spieler (2016).
\emph{The Quarterly Journal of Experimental Psychology}, \emph{70},
1792--1807.
doi:\href{https://doi.org/10.1080/17470218.2016.1206130}{10.1080/17470218.2016.1206130}

\hypertarget{ref-crump_context-specific_2006}{}
Crump, M. J., Gong, Z., \& Milliken, B. (2006). The context-specific
proportion congruent Stroop effect: Location as a contextual cue.
\emph{Psychonomic Bulletin \& Review}, \emph{13}, 316--321.
doi:\href{https://doi.org/10.3758/BF03193850}{10.3758/BF03193850}

\hypertarget{ref-crump_context-specific_2008}{}
Crump, M. J., Vaquero, J. M., \& Milliken, B. (2008). Context-specific
learning and control: The roles of awareness, task relevance, and
relative salience. \emph{Consciousness and Cognition}, \emph{17},
22--36.
doi:\href{https://doi.org/10.1016/j.concog.2007.01.004}{10.1016/j.concog.2007.01.004}

\hypertarget{ref-devine_stereotypes_1989}{}
Devine, P. G. (1989). Stereotypes and prejudice: Their automatic and
controlled components. \emph{Journal of Personality and Social
Psychology}, \emph{56}(1), 5.

\hypertarget{ref-egner_creatures_2014}{}
Egner, T. (2014). Creatures of habit (and control): A multi-level
learning perspective on the modulation of congruency effects.
\emph{Frontiers in Psychology}, \emph{5}, 1247.
doi:\href{https://doi.org/10.3389/fpsyg.2014.01247}{10.3389/fpsyg.2014.01247}

\hypertarget{ref-eriksen_effects_1974}{}
Eriksen, B. A., \& Eriksen, C. W. (1974). Effects of noise letters upon
the identification of a target letter in a nonsearch task.
\emph{Perception \& Psychophysics}, \emph{16}, 143--149.
doi:\href{https://doi.org/10.3758/BF03203267}{10.3758/BF03203267}

\hypertarget{ref-fischer_predicting_2015}{}
Fischer, R., \& Dreisbach, G. (2015). Predicting high levels of
multitasking reduces between-tasks interactions., \emph{41}, 1482--1487.
Retrieved from \url{http://psycnet.apa.org/psycinfo/2015-47211-001/}

\hypertarget{ref-fischer_context-sensitive_2014}{}
Fischer, R., Gottschalk, C., \& Dreisbach, G. (2014). Context-sensitive
adjustment of cognitive control in dual-task performance. \emph{Journal
of Experimental Psychology: Learning, Memory, and Cognition}, \emph{40},
399.

\hypertarget{ref-fiske_continuum_1990}{}
Fiske, S. T., \& Neuberg, S. L. (1990). A continuum of impression
formation, from category-based to individuating processes: Influences of
information and motivation on attention and interpretation. In
\emph{Advances in experimental social psychology} (Vol. 23, pp. 1--74).
Elsevier.

\hypertarget{ref-hutcheon_limits_2017}{}
Hutcheon, T. G., \& Spieler, D. H. (2017). Limits on the
generalizability of context-driven control. \emph{Quarterly Journal of
Experimental Psychology}, \emph{70}, 1292--1304.
doi:\href{https://doi.org/10.1080/17470218.2016.1182193}{10.1080/17470218.2016.1182193}

>>>>

\shorttitle{Contextual recruitment of selective attention}
\affiliation{
\vspace{0.5cm}
\textsuperscript{1} The Graduate Center of the City University of New York\\\textsuperscript{2} Brooklyn College of the City University of New York}
\keywords{Attention, Memory, Cognitive Control, Conflict Adaptation, Context-specific, Task Relevance\newline\indent Word count: 4024 \vspace{2mm} \par \textit{Public Significance Statement:} Contextual cues have been shown to automatically trigger adjustments in selective attention independent of awareness and intention. Here, we find that task-relevance plays an important role in determining which context cues are used to direct attention. These findings contribute to a better understanding of how context-dependency might occur in more complex environments and more generally, how learning and memory processes enable flexible control over attention.}
\usepackage{csquotes}
\usepackage{upgreek}
\captionsetup{font=singlespacing,justification=justified}

@@

\makeatletter
\newcommand\LastLTentrywidth{1em}
\newlength\longtablewidth
\setlength{\longtablewidth}{1in}
\newcommand{\getlongtablewidth}{\begingroup \ifcsname LT@\roman{LT@tables}\endcsname \global\longtablewidth=0pt \renewcommand{\LT@entry}[2]{\global\advance\longtablewidth by ##2\relax\gdef\LastLTentrywidth{##2}}\@nameuse{LT@\roman{LT@tables}} \fi \endgroup}
\usepackage{setspace}\doublespacing
\newenvironment{zeroindent} {\par\setlength{\parindent}{0pt}} {\par}
\setlength{\parskip}{0pt}
\raggedbottom

@@

\abstract{
Evidence across a wide variety of attention paradigms shows that environmental cues can trigger adjustments to ongoing priorities for attending to relevant and irrelevant information. This context-specific control over attention suggests that cognitive control can be both automatic and flexible. For instance, in selective attention tasks, congruency effects are larger for items that appear in a context associated with infrequent conflict than in a context associated with frequent conflict. Since the to-be-presented context cannot be predicted or prepared for in advance, attention is assumed to be rapidly updated on-the-fly, triggered by the currently presented context. Context-specific control exemplifies how learning and memory processes can influence attention to enable cognitive flexibility. However, what determines the use of previously learned associations still remains unclear. In the current study, we examined whether task-relevance would influence the learning and use of context cues in a flanker task. Using a secondary counting task, context dimensions associated with differing levels of conflict were made task-relevant or -irrelevant across the experiment. In short, we found that making new contextual information task-relevant caused participants to ignore a previously learned context-attention association and adopt a new context-specific control strategy; all without changing the experimental stimuli. This result suggests that task-relevance is a key determinant of context-specific control.

}

@@

Selective attention is commonly investigated using interference paradigms such as the Stroop (1935) and flanker (Eriksen \& Eriksen, 1974) tasks, where participants identify a target while ignoring a response-congruent or -incongruent distractor. Performance is typically better on congruent versus incongruent trials and the difference---the congruency effect---taken as an index of attentional priorities. Large congruency effects are thought to reflect ineffective filtering of the distracting stimuli whereas small congruency effects are thought to reflect effective filtering. By probing factors that systematically alter congruency effects, we can then make inferences about processes that control attentional filtering. For example, manipulating the frequency of conflict via the proportion of congruent versus incongruent trials has shown to influence the size of the congruency effect. Typically, a high proportion congruent experiment produces large congruency effects, whereas a low proportion congruent experiment produces small congruency effects (Logan \& Zbrodoff, 1979; Lowe \& Mitterer, 1982; West \& Baylis, 1998). This result is usually explained as strategic control, where participants increase attentional control under high-conflict demands and relax attentional control under low-conflict demands (Logan, 1980; Logan \& Zbrodoff, 1979; Logan, Zbrodoff, \& Williamson, 1984; Lowe \& Mitterer, 1982). Recent work however, has demonstrated that attentional control is not only adjusted by top-down regulation, but can also be triggered automatically by environmental cues (Brosowsky \& Crump, 2018; Bugg \& Crump, 2012; Egner, 2014; Fischer \& Dreisbach, 2015; King, Korb, \& Egner, 2012; Mayr \& Bryck, 2007).

For example, Crump, Gong, and Milliken (Crump, Gong, \& Milliken, 2006; see also, Corballis \& Gratton, 2003) presented Stroop stimuli in one of two randomly chosen locations and manipulated the frequency of conflict associated with each location. One location was associated with a high frequency of conflict (25\% congruent trials) and the other with a low frequency of conflict (75\% congruent trials). Overall, the proportion of congruent trials was 50\% and randomized such that the upcoming location could not be predicted. Even so, congruency effects were shown to be smaller for trials where the stimulus appeared in the high conflict location as compared to the low conflict location. This effect, known now as the context-specific proportion congruent effect (CSPC), has now been replicated in a number of different selective attention paradigms (e.g., Alards-Tomalin, Brosowsky, \& Mondor, 2017; Blais, Harris, Sinanian, \& Bunge, 2015; Bugg, 2014; Crump, 2016; Crump, Milliken, Leboe-McGowan, Leboe-McGowan, \& Gao, 2018; Fischer, Gottschalk, \& Dreisbach, 2014; Hübner \& Mishra, 2016).

Critical evidence however, that CSPC effects reflect context-specific control rather than other non-control learning processes (e.g., Schmidt \& Besner, 2008), comes from work showing that CSPC effects can transfer to frequency unbiased items (Brosowsky \& Crump, 2016; Crump \& Milliken, 2009; Weidler \& Bugg, 2016; Weidler, Dey, \& Bugg, 2018; though, see Hutcheon \& Spieler, 2017). Crump and Milliken (2009), for example, divided Stroop items into two mutually exclusive sets (e.g., RED/GREEN and BLUE/YELLOW). One set was defined as the frequency biased set, and presented with 75\% congruency in one location, and 25\% congruency in the other. The second set however, was presented with 50\% congruency in both locations. Nevertheless, they found smaller congruency effects for unbiased items presented in the high conflict location as compared to the low conflict location.

@@

\hypertarget{the-current-study}{%
\section{The Current Study}\label{the-current-study}}

@@

A flanker task was used to measure attentional control in an adapted CSPC design (Crump, Brosowsky, \& Milliken, 2017; Crump \& Milliken, 2009). Similar to previous studies, flanker stimuli were presented in contexts associated with differing levels of conflict (0\%, 50\%, or 100\% congruent). However, unlike previous CSPC designs where contexts were defined by a single discriminating feature (e.g., upper vs.~lower screen locations), contexts were defined by two feature dimensions (see Figure 1A). In one condition, for example, contexts were defined by object identity (hat or chair) and color (blue or green). Only three out of the four possible feature combinations were presented, each associated with a different proportion of congruent trials (0\%, 50\%, or 100\% congruent). Critically, the frequency unbiased context (50\% congruent) always shared a feature with each of the frequency-biased contexts (0\% and 100\% congruent). The frequency biased contexts (0\% and 100\% congruent) however, did not share any features (see Figure 1C for an example).

@@

\hypertarget{methods}{%
\section{Methods}\label{methods}}

@@

\hypertarget{participants}{%
\subsection{Participants}\label{participants}}

@@

\hypertarget{apparatus-stimuli}{%
\subsection{Apparatus \& Stimuli}\label{apparatus-stimuli}}

@@

\hypertarget{design}{%
\subsection{Design}\label{design}}

@@

\hypertarget{results}{%
\section{Results}\label{results}}

@@

\hypertarget{general-discussion}{%
\section{General Discussion}\label{general-discussion}}

@@

In light of prior work, we take this as evidence that the contextual recruitment of selective attention, although likely implicit, is not obligatory (e.g., Brosowsky \& Crump, 2016), requiring that environmental information be incorporated into the task representation. Similarly, there appears to be flexibility in which environmental features are selected and used to guide attention, which can be rapidly updated depending on the task-relevance of those features. Such a result lends some insight into how context-specific control might operate in more complex, real-world environments, where there is an over-abundance of environmental features that afford many different learned associations. From a theoretical perspective, this result is consistent memory-based accounts of CSPC phenomena (Brosowsky \& Crump, 2018; Bugg \& Hutchison, 2013; Crump et al., 2017, 2018; Crump \& Milliken, 2009). Under this view, a memory process encodes attentional priorities in the representation of individual experiences and, as a result, become associated with the environment where they were used. The subsequent reoccurrence of a prior context triggers the retrieval and reinstatement of those attentional priorities. Our results show however, that all the features of the environment may not be treated equally and that only task-relevant features are used to probe memory and guide attention.

@@

\hypertarget{refs}{}
\leavevmode\hypertarget{ref-abrahamse_grounding_2016}{}%
Abrahamse, E., Braem, S., Notebaert, W., \& Verguts, T. (2016). Grounding cognitive control in associative learning. \emph{Psychological Bulletin}, \emph{142}, 693--728. doi:\href{https://doi.org/10.1037/bul0000047}{10.1037/bul0000047}

\leavevmode\hypertarget{ref-alards-tomalin_auditory_2017}{}%
Alards-Tomalin, D., Brosowsky, N. P., \& Mondor, T. A. (2017). Auditory statistical learning: Predictive frequency information affects the deployment of contextually mediated attentional resources on perceptual tasks. \emph{Journal of Cognitive Psychology}, \emph{29}, 977--987. doi:\href{https://doi.org/10.1080/20445911.2017.1353518}{10.1080/20445911.2017.1353518}

\leavevmode\hypertarget{ref-blais_trial-by-trial_2015}{}%
Blais, C., Harris, M. B., Sinanian, M. H., \& Bunge, S. A. (2015). Trial-by-trial adjustments in control triggered by incidentally encoded semantic cues. \emph{The Quarterly Journal of Experimental Psychology}, \emph{68}, 1920--1930. doi:\href{https://doi.org/10.1080/17470218.2014.1000346}{10.1080/17470218.2014.1000346}

\leavevmode\hypertarget{ref-brady_visual_2013}{}%
Brady, T. F., Konkle, T., Gill, J., Oliva, A., \& Alvarez, G. A. (2013). Visual long-term memory has the same limit on fidelity as visual working memory. \emph{Psychological Science}, \emph{24}, 981--990. doi:\href{https://doi.org/10.1177/0956797612465439}{10.1177/0956797612465439}

\leavevmode\hypertarget{ref-brewer_dual_1988}{}%
Brewer, M. B. (1988). A dual process model of impression formation. In R. S. Wyer Jr \& T. K. Srull (Eds.), \emph{A dual-process model of impression formation: Advances in social cognition} (Vol. 1, pp. 1--36). Hillsdale, NJ: Erlbaum.

\leavevmode\hypertarget{ref-brosowsky_context-specific_2016}{}%
Brosowsky, N. P., \& Crump, M. J. (2016). Context-specific attentional sampling: Intentional control as a pre-requisite for contextual control. \emph{Consciousness and Cognition}, \emph{44}, 146--160. doi:\href{https://doi.org/10.1016/j.concog.2016.07.001}{10.1016/j.concog.2016.07.001}

\leavevmode\hypertarget{ref-brosowsky_memory-guided_2018}{}%
Brosowsky, N. P., \& Crump, M. J. C. (2018). Memory-guided selective attention: Single experiences with conflict have long-lasting effects on cognitive control. \emph{Journal of Experimental Psychology: General}, \emph{147}, 1134--1153. doi:\href{https://doi.org/10.1037/xge0000431}{10.1037/xge0000431}

\leavevmode\hypertarget{ref-bugg_conflict-triggered_2014}{}%
Bugg, J. (2014). Conflict-triggered top-down control: Default mode, last resort, or no such thing? \emph{Journal of Experimental Psychology: Learning, Memory, and Cognition}, \emph{40}(2), 567.

\leavevmode\hypertarget{ref-bugg_support_2012}{}%
Bugg, J., \& Crump, M. J. (2012). In support of a distinction between voluntary and stimulus-driven control: A review of the literature on proportion congruent effects. \emph{Frontiers in Psychology}, \emph{3}, 367. doi:\href{https://doi.org/10.3389/fpsyg.2012.00367}{10.3389/fpsyg.2012.00367}

\leavevmode\hypertarget{ref-bugg_converging_2013}{}%
Bugg, J., \& Hutchison, K. A. (2013). Converging evidence for control of color--word Stroop interference at the item level. \emph{Journal of Experimental Psychology: Human Perception and Performance}, \emph{39}(2), 433.

\leavevmode\hypertarget{ref-bugg_multiple_2008}{}%
Bugg, J., Jacoby, L. L., \& Toth, J. P. (2008). Multiple levels of control in the Stroop task. \emph{Memory \& Cognition}, \emph{36}, 1484--1494. doi:\href{https://doi.org/10.3758/MC.36.8.1484}{10.3758/MC.36.8.1484}

\leavevmode\hypertarget{ref-canadas_social_2013}{}%
Cañadas, E., Rodríguez-Bailón, R., Milliken, B., \& Lupiáñez, J. (2013). Social categories as a context for the allocation of attentional control. \emph{Journal of Experimental Psychology: General}, \emph{142}, 934--943. doi:\href{https://doi.org/10.1037/a0029794}{10.1037/a0029794}

\leavevmode\hypertarget{ref-corballis_independent_2003}{}%
Corballis, P. M., \& Gratton, G. (2003). Independent control of processing strategies for different locations in the visual field. \emph{Biological Psychology}, \emph{64}, 191--209. doi:\href{https://doi.org/10.1016/S0301-0511(03)00109-1}{10.1016/S0301-0511(03)00109-1}

\leavevmode\hypertarget{ref-crisp_multiple_2007}{}%
Crisp, R. J., \& Hewstone, M. (2007). Multiple social categorization. \emph{Advances in Experimental Social Psychology}, \emph{39}, 163--254.

\leavevmode\hypertarget{ref-crump_learning_2016}{}%
Crump, M. J. (2016). Learning to selectively attend from context-specific attentional histories: A demonstration and some constraints. \emph{Canadian Journal of Experimental Psychology/Revue Canadienne de Psychologie Expérimentale}, \emph{70}, 59--77. doi:\href{https://doi.org/10.1037/cep0000066}{10.1037/cep0000066}

\leavevmode\hypertarget{ref-crump_reproducing_2017}{}%
Crump, M. J., Brosowsky, N. P., \& Milliken, B. (2017). Reproducing the location-based context-specific proportion congruent effect for frequency unbiased items: A reply to Hutcheon and Spieler (2016). \emph{The Quarterly Journal of Experimental Psychology}, \emph{70}, 1792--1807. doi:\href{https://doi.org/10.1080/17470218.2016.1206130}{10.1080/17470218.2016.1206130}

\leavevmode\hypertarget{ref-crump_flexibility_2009}{}%
Crump, M. J. C., \& Milliken, B. (2009). The flexibility of context-specific control: Evidence for context-driven generalization of item-specific control settings. \emph{The Quarterly Journal of Experimental Psychology}, \emph{62}, 1523--1532. doi:\href{https://doi.org/10.1080/17470210902752096}{10.1080/17470210902752096}

\leavevmode\hypertarget{ref-crump_context-dependent_2018}{}%
Crump, M. J. C., Milliken, B., Leboe-McGowan, J., Leboe-McGowan, L., \& Gao, X. (2018). Context-Dependent Control of Attention Capture: Evidence From Proportion Congruent Effects. \emph{Canadian Journal of Experimental Psychology= Revue Canadienne de Psychologie Experimentale}, \emph{74}, 91--104.

\leavevmode\hypertarget{ref-crump_context-specific_2006}{}%
Crump, M. J., Gong, Z., \& Milliken, B. (2006). The context-specific proportion congruent Stroop effect: Location as a contextual cue. \emph{Psychonomic Bulletin \& Review}, \emph{13}, 316--321. doi:\href{https://doi.org/10.3758/BF03193850}{10.3758/BF03193850}

\leavevmode\hypertarget{ref-crump_context-specific_2008}{}%
Crump, M. J., Vaquero, J. M., \& Milliken, B. (2008). Context-specific learning and control: The roles of awareness, task relevance, and relative salience. \emph{Consciousness and Cognition}, \emph{17}, 22--36. doi:\href{https://doi.org/10.1016/j.concog.2007.01.004}{10.1016/j.concog.2007.01.004}

\leavevmode\hypertarget{ref-devine_stereotypes_1989}{}%
Devine, P. G. (1989). Stereotypes and prejudice: Their automatic and controlled components. \emph{Journal of Personality and Social Psychology}, \emph{56}(1), 5.

\leavevmode\hypertarget{ref-egner_creatures_2014}{}%
Egner, T. (2014). Creatures of habit (and control): A multi-level learning perspective on the modulation of congruency effects. \emph{Frontiers in Psychology}, \emph{5}, 1247. doi:\href{https://doi.org/10.3389/fpsyg.2014.01247}{10.3389/fpsyg.2014.01247}

\leavevmode\hypertarget{ref-eriksen_effects_1974}{}%
Eriksen, B. A., \& Eriksen, C. W. (1974). Effects of noise letters upon the identification of a target letter in a nonsearch task. \emph{Perception \& Psychophysics}, \emph{16}, 143--149. doi:\href{https://doi.org/10.3758/BF03203267}{10.3758/BF03203267}

\leavevmode\hypertarget{ref-fischer_predicting_2015}{}%
Fischer, R., \& Dreisbach, G. (2015). Predicting high levels of multitasking reduces between-tasks interactions., \emph{41}, 1482--1487. Retrieved from \url{http://psycnet.apa.org/psycinfo/2015-47211-001/}

\leavevmode\hypertarget{ref-fischer_context-sensitive_2014}{}%
Fischer, R., Gottschalk, C., \& Dreisbach, G. (2014). Context-sensitive adjustment of cognitive control in dual-task performance. \emph{Journal of Experimental Psychology: Learning, Memory, and Cognition}, \emph{40}, 399.

\leavevmode\hypertarget{ref-fiske_continuum_1990}{}%
Fiske, S. T., \& Neuberg, S. L. (1990). A continuum of impression formation, from category-based to individuating processes: Influences of information and motivation on attention and interpretation. In \emph{Advances in experimental social psychology} (Vol. 23, pp. 1--74). Elsevier.

\leavevmode\hypertarget{ref-hutcheon_limits_2017}{}%
Hutcheon, T. G., \& Spieler, D. H. (2017). Limits on the generalizability of context-driven control. \emph{Quarterly Journal of Experimental Psychology}, \emph{70}, 1292--1304. doi:\href{https://doi.org/10.1080/17470218.2016.1182193}{10.1080/17470218.2016.1182193}
